---
title: ""
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
header-includes:
  - \usepackage{geometry}
  - \geometry{margin=0.75in}
  - \usepackage{fancyhdr}
  - \usepackage{xcolor}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \definecolor{brandpurple}{HTML}{667eea}
  - \definecolor{darkbg}{HTML}{1a202c}
  - \definecolor{lightgrey}{HTML}{a0aec0}
  - \definecolor{darktext}{HTML}{2d3748}
  - \definecolor{scoregreen}{HTML}{48bb78}
  - \definecolor{scoreyellow}{HTML}{ecc94b}
  - \definecolor{scorered}{HTML}{fc8181}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[L]{\textcolor{lightgrey}{\small AiRR Brand Intelligence Report}}
  - \fancyhead[R]{\textcolor{lightgrey}{\small \today}}
  - \fancyfoot[C]{\textcolor{lightgrey}{\small Page \thepage}}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\headrule}{\hbox to\headwidth{\color{brandpurple}\leaders\hrule height \headrulewidth\hfill}}
params:
  brand_name: "Brand"
  report_type: "brand"
  prompt_text: ""
  ai_summary: ""
  rankings_data: NULL
  trend_plot_path: ""
  spider_plot_path: ""
  generated_at: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.pos = "H")
library(knitr)
```

\begin{center}
{\fontsize{28}{34}\selectfont \textcolor{brandpurple}{\textbf{AiRR}}} \\[6pt]
{\fontsize{14}{18}\selectfont \textcolor{darktext}{Brand Intelligence Report}} \\[12pt]
{\fontsize{18}{22}\selectfont \textbf{`r params$brand_name`}} \\[6pt]
{\small \textcolor{lightgrey}{Generated `r params$generated_at`}}
\end{center}

\vspace{8pt}
\noindent\textcolor{brandpurple}{\rule{\textwidth}{2pt}}
\vspace{12pt}

```{r conditional-prompt-header, results='asis'}
if (params$report_type == "prompt" && nchar(params$prompt_text) > 0) {
  cat(paste0(
    "\\noindent{\\small \\textcolor{lightgrey}{TRACKING PROMPT}} \\\\[4pt]\n",
    "\\noindent{\\large \\textit{``", gsub("([#$%&_{}~^\\\\])", "\\\\\\1", params$prompt_text), "''}} \\\\[12pt]\n"
  ))
}
```

## Executive Summary

```{r ai-summary, results='asis'}
if (nchar(params$ai_summary) > 0) {
  # Split into paragraphs and output
  paragraphs <- strsplit(params$ai_summary, "\n\n|\n")[[1]]
  paragraphs <- paragraphs[nchar(trimws(paragraphs)) > 0]
  for (p in paragraphs) {
    cat(p, "\n\n")
  }
} else {
  cat("\\textcolor{lightgrey}{\\textit{No AI analysis available. Generate one from the dashboard before exporting.}}")
}
```

\vspace{12pt}

## Performance Overview

```{r trend-chart, fig.width=8, fig.height=4, fig.cap="Score trends over time", out.width="100%"}
if (file.exists(params$trend_plot_path)) {
  knitr::include_graphics(params$trend_plot_path)
} else {
  cat("\\textcolor{lightgrey}{\\textit{Trend chart not available.}}")
}
```

```{r spider-chart, fig.width=5, fig.height=4.5, fig.cap="Brand comparison radar", out.width="70%", fig.align="center"}
if (file.exists(params$spider_plot_path)) {
  knitr::include_graphics(params$spider_plot_path)
} else {
  cat("\\textcolor{lightgrey}{\\textit{Comparison chart not available.}}")
}
```

\vspace{12pt}

## Brand Rankings

```{r rankings-table, results='asis'}
if (!is.null(params$rankings_data) && nrow(params$rankings_data) > 0) {
  
  display_data <- params$rankings_data
  display_data$Brand <- ifelse(
    display_data$is_main,
    paste0("* ", display_data$brand_name, " (Your Brand)"),
    paste0("  ", display_data$brand_name)
  )
  
  display_data <- display_data[order(-display_data$airr_score), ]
  display_data$Rank <- seq_len(nrow(display_data))
  
  table_data <- data.frame(
    Rank = display_data$Rank,
    Brand = display_data$Brand,
    AiRR = round(display_data$airr_score, 1),
    Presence = round(display_data$presence_score, 1),
    Perception = round(display_data$perception_score, 1),
    Prestige = round(display_data$prestige_score, 1),
    Persistence = round(display_data$persistence_score, 1),
    stringsAsFactors = FALSE
  )
  
  kable(table_data, format = "latex", booktabs = TRUE, 
        align = c("c", "l", "c", "c", "c", "c", "c"),
        linesep = "") |>
    kableExtra::kable_styling(
      latex_options = c("hold_position", "striped"),
      full_width = TRUE,
      font_size = 10
    )
} else {
  cat("\\textcolor{lightgrey}{\\textit{No ranking data available.}}")
}
```

\vspace{20pt}
\noindent\textcolor{brandpurple}{\rule{\textwidth}{1pt}}
\vspace{6pt}

\begin{center}
{\small \textcolor{lightgrey}{This report was generated by AiRR — AI Reputation \& Readiness scoring.}} \\
{\small \textcolor{lightgrey}{Scores are based on analysis of AI model responses and may vary over time.}}
\end{center}